Datasheet for Wordbank

### 2024-12-02 other/datasheet/datasheet_wordbank.qmd
Typo updated.

	- The dataset is a sample drawn from responses using CDI across various languages. Norming samples were obtained through a probabilistic sampling strategy to ensure demographic representativeness, balancing factors such as age, gender, and region, and providing a standardized baseline for language acquisition. In contrast, non-norming samples were collected using convenience or purposive sampling, often targeting specific populations or linguistic environments to enhance diversity. While the norming samples support generalizations and cross-study comparisons, the non-norming samples offer valuable insights into underrepresented contexts, together creating a comprehensive resource for studying early vocabulary development.

>>>>

	- The dataset is a sample drawn from responses using CDI across various languages. Norming samples were obtained through a probabilistic sampling strategy to ensure demographic representativeness, balancing factors such as age, gender, and region, and providing a standardized baseline for language acquisition. In contrast, non-norming samples were collected using convenience or purposive sampling, often targeting specific populations or linguistic environments to enhance diversity. While the norming samples support generalizations and cross-study comparisons, the non-norming samples offer investigations into underrepresented contexts, together creating a comprehensive resource for studying early vocabulary development.
